Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-02 paper/EDA.qmd
Updated dataset

---
title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
subtitle: "Exploratory Data Analysis (EDA)"
author: 
  - Navya Hooda
  - Mohammed Yusuf Shaikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
---

@@

>>>>

---
title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
subtitle: "Exploratory Data Analysis (EDA)"
author: 
  - Navya Hooda
  - Mohammed Yusuf Shaikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
bibliography: references.bib
---

@@

# Assumptions
